---
title: "Bochao"
output: html_notebook
---
Environment for ASN2
```{r}
library(dplyr)
library(Hmisc)
library(psych)
```

Exercise 1a
Loading the data set
```{r}
ds <- read.csv(file="bank-additional-full.csv",sep=';')
```

Exercise 2a
General descriptive statistics
```{r}
summary(ds)
```

Exercise 2b
There are 7.15% cases being removed. (Less than 10%)
```{r}
ol <- nrow(ds)
ds[which(ds$job == "unknown"),"job"]<-NA
ds[which(ds$marital == "unknown"),"marital"]<-NA
ds[which(ds$education == "unknown"),"education"]<-NA
ds[which(ds$housing == "unknown"),"housing"]<-NA
ds[which(ds$loan == "unknown"),"loan"]<-NA

ds <- na.omit(ds)
ne <- nrow(ds)
red_rate <- (ol-ne)/ol
red_rate
```

Exercise 2c
Age Category is created
```{r}
youth <- seq(0,18)
young_adult <- seq(19,34)
adult <- seq(35,59)
senior <- seq(60,100)

ds$cat_age <- ifelse(ds$age %in% youth, "youth",
             ifelse(ds$age %in% young_adult, "young adult",
             ifelse(ds$age %in% adult, "adult",
             ifelse(ds$age %in% senior, "senior",
              NA))))
```

Exercise 2c
Distinguish old and new client
```{r}
ds$client_NewOld <- ifelse(ds$poutcome == "nonexistent", "new client",
                    ifelse(ds$poutcome == "failure", "old client",
                    ifelse(ds$poutcome == "success", "old client",NA)))
ds
```

Exercise 2d
General summary of 'age' by each 'job's
```{r}
describeBy(ds$age, ds$job)
```

Exercise 2e
Finds the mode of 'moth', the result is 'may' as the result shown
```{r}
mode <- names(sort(table(ds$month)))[length(table(ds$month))]
mode
```

Exercise 2f
As the result shown
mean = 258.21
median = 180
variance = 67492.22
inter-quartile range: 217
```{r}
mean(ds$duration)
median(ds$duration)
var(ds$duration)
IQR(ds$duration)
```

Exercise 2g
```{r}
group_by(ds,cat_age) %>% summarise(mean=mean(campaign),sd=sd(campaign),.groups='drop')
group_by(ds,y) %>% summarise(mean=mean(campaign),sd=sd(campaign),.groups='drop')
group_by(ds,cat_age,y) %>% summarise(mean=mean(campaign),sd=sd(campaign),.groups='drop')
```

Exercise 2h
In desending order
```{r}
group_by(ds,marital,education) %>% tally(sort = TRUE)
```

Exercise 2i
As the result shown,
the 3 days of the week where most contacts are made for persons with “single” as marital status are:
Thursday
Wednesday
Friday
```{r}
tb <- table(ds$day_of_week,ds$marital)
tb
ratio <- sort(tb[,3]/(tb[,1]+tb[,2]+tb[,3]),decreasing = TRUE)
ratio
#ratio is the proportion of the 'single' in the 'day_of_week'
names(alt[c(1,2,3)])
```

Exercise 2j
As the result shown,
there are 2220 outliers in the column 'campaign'
```{r}
iqr <- IQR(ds$campaign)
lowq <- quantile(ds$campaign)[2]-iqr*1.5
highq <- quantile(ds$campaign)[4]+iqr*1.5
nrow(subset(ds, campaign>highq | campaign<lowq))
```

Exercise 2k
The following table shows the information of the cases whose column 'age' is considered as outliers
```{r}
iqr <- IQR(ds$age)
lowq <- quantile(ds$age)[2]-iqr*1.5
highq <- quantile(ds$age)[4]+iqr*1.5
sub <- subset(ds, age>highq | age<lowq)
sub
nrow(sub)
mean(sub$age)
median(sub$age)
```

Exercise 2l
A table indicates the number of outliers with 'euribor3m' value larger than 1.5 for each typr of 'client_NewOld' and 'cat_age'
```{r}
iqr <- IQR(ds$campaign)
lowq <- quantile(ds$campaign)[2]-iqr*1.5
highq <- quantile(ds$campaign)[4]+iqr*1.5
sub <- subset(ds, (campaign>highq | campaign<lowq) & euribor3m>1.5)
table(sub$cat_age,sub$client_NewOld)
```

Exercise 2m
Plot shows the frequncy of each type of job with barplot
```{r}
freq <- table(ds$job)
barplot(freq,las=2, cex.names=1)
```

Exercise 2n
```{r}
theme_update(text = element_text(size=8))
ggplot(ds, aes(job,fill=y))+geom_bar(position = 'dodge')
```

Exercise 2o
```{r}
ggplot(ds, aes(age,fill=default))+geom_density(alpha=.5)
```

Exercise 2p
According to the following plot,
the data in 'duration' follows a right-skewed pattern normal distribution generally, 
with the density curve shown in the plot 
```{r}
ggplot(ds, aes(duration))+geom_histogram(aes(y = ..density..),fill='blue',color='darkblue',alpha=.5,bins=100)+geom_density(color='darkblue',size=1)+xlim(0,1000)
```

Exercise 2q
```{r}
ggplot(ds,aes(x=duration,y=y,fill=client_NewOld))+geom_boxplot()
```

Exercise 3
Founding #1:
According to the two following plots,
we can find most people have much more housing loan instead of personal loan
```{r}
ggplot(ds, aes(job,fill=loan))+geom_bar(position = 'dodge')
ggplot(ds, aes(job,fill=housing))+geom_bar(position = 'dodge')
```
Founding #2:
Jobs like admin tend to be formed with employees with university degree (high level degree),
Professional courses helps people getting technical jobs,
```{r}
ggplot(ds, aes(job,fill=education))+geom_bar(position = 'dodge')
```
Founding #3:
Most of the unmarried people are formed with young adult and adult,
Marriage and divorced happen in the adult age mainly
```{r}
ggplot(ds, aes(age,fill=marital))+geom_density(alpha=.5)
```
