---
title: "Bochao"
output: html_notebook
---
### Environment
```{r}
library(readr)
library(dplyr)
library(ggplot2)
library(mlbench)
library(cluster)
library(fpc)
library(reshape2)
library(DMwR)
```

### 1. Load Data
```{r}
dt <- read.csv("buddymove_holidayiq.csv",header = TRUE)
dt <- dt[,2:7]
```

### 2. Determin K values
With the following plots, we can know that average silhouette reaches max at K=3, therefore, optimal K value is 3.
```{r}
set.seed(1234)
preA <-c()
for(i in 2:10){
  rr <- kmeans(dt,centers = i,iter.max = 200)
  sua <- silhouette(rr$cluster,dist(dt))
  preA <- c(preA,mean(sua[,3]))
}
ggplot(data.frame(nc=2:10,ns=preA),
       aes(x=nc,y=ns))+geom_point(size=4,color="blue")+geom_line()+
       xlab("Data Clusters")+ylab("Silhouette Coefficient")
```

### 3. Anaylize K-mean
```{r}
clusters <- kmeans(dt,centers = 3,iter.max = 200)
forp <- silhouette(clusters$cluster,dist(dt))
plot(forp,border=NA)
```

### 4. Analyize PAM
```{r}
clusters <- pam(dt,k=3)
plot(clusters)
forp <- silhouette(clusters$clustering,dist(dt))
plot(forp,col="grey",border = NA)
```

### 5. CLARA
With the following result, we can see that 3 clusters is the optimal choice.
```{r}
set.seed(1234)
preA <-c()
for(i in 2:10){
  rr <- clara(dt,i)
  sua <- silhouette(rr$cluster,dist(dt))
  preA <- c(preA,mean(sua[,3]))
}
ggplot(data.frame(nc=2:10,ns=preA),
       aes(x=nc,y=ns))+geom_point(size=4,color="blue")+geom_line()+
       xlab("Data Clusters")+ylab("Silhouette Coefficient")
```


### 6.CLARA result
```{r}
clb <- clara(dt,3)
clusplot(clb)
```

### 7. Analyize CLARA
```{r}
forp <- silhouette(clb$clustering,dist(dt))
plot(forp,col="grey",border = NA)
```

### 8. DBSCAN
```{r}
preDb <- scale(dt)
db <- dbscan(preDb,0.9,10)
plot(db,preDb)
forp <- silhouette(db$cluster,dist(preDb))
plot(forp,border = NA)
```

### 9. Hierarchical clustring
With the following plot, we can see that using single or average method and 2 clusters is our optimal choice.
```{r}
preDb <- dist(scale(dt))
alts <- c('complete','single','average')
preA <- matrix(NA,ncol=3,nrow=9,dimnames=list(2:10,alts))

for(i in 2:10){
  for(m in seq_along(alts)){
    height <- hclust(preDb,meth=alts[m])
    c<-cutree(height,i)
    sua <- silhouette(c,preDb)
    preA[i-1,m] <- mean(sua[,3])
  }
}

preDt <- melt(preA)
colnames(preDt) <- c("Nclusters","Method","Result")
ggplot(preDt,aes(x=Nclusters,y=Result,color=Method))+geom_line()
```

### 10. Analyize Hierarchical clustring
```{r}
preDb <- dist(scale(dt))
height <- hclust(preDb, method = "complete")
cls <- cutree(height,2)
plot(height)

frp <- silhouette(cls,preDb)
plot(frp,border=NA)
```

### 11. Summarize all results for clustring
With all results above, we get  
1. k-means with k=3, silhouette = 0.35  
2. CLARA with 3 clusters, silhouette = 0.34  
3. DBSCAN, silhouette = 0.02  
4. Hierarchical clustering with single or average method, with 2 clusters, silhouette = 0.4  
  
As a result, we believe that using Hierarchical clustering with single or average method, with tree cut in 2, is our best choice to complete the task.  

### 12. Outlier Detection with IQR
Number of outliers in different column is shown in the following table.
```{r}
ocs <- c(0,0,0,0,0,0)
for(i in 1:6){
  tem <- IQR(dt[,i])
  qt <- quantile(dt[,i])
  q1 <- qt[2]
  q3 <- qt[4]
  counter <- 0
  for(k in 1:nrow(dt)){
    if( (dt[k,i] < (q1-1.5*tem)) | (dt[k,i] > (q3+1.5*tem)) ){
      counter <- counter + 1
      print(k)
    }
    ocs[i]<-counter
  }
}
data.frame(ocs,colnames(dt))
boxplot(dt)
```

### 13. DBSCAN outlier detection
Following result are the number of outliers using DBSCAN
```{r}
otp <- scale(dt)
odb <- dbscan(otp,1)
which(odb$cluster==0)
```

### 14. LOF outlier detection
Following results are the outlier presented by the case number  
Lof score threshold is set to be 1.3
```{r}
lof <- lofactor(dt,3)
which(lof>1.3)
```

### 15. Outlier ranking
Following results are the outlier presented by the case number  
First 10 in the rank is considered to be outliers
```{r}
or <- outliers.ranking(dt)
#round(or$prob.outliers,3)
head(order(or$rank.outliers,decreasing = TRUE),10)
```
